---
title: "DateandTimeHW"
author: "Venkata Dhanush Kikkisetti"
date: "2023-01-23"
output: pdf_document
---

## 1  Use and show R coding to find the number of days from June 6th 2020 to July 14th 2021  
```{r}
library(tidyverse)
library(lubridate)
library(nycflights13)
(dmy("06-06-2020")%--%dmy("14-07-2021"))%/%days(1)
```

## 2 Use and show R coding to confirm that the year 1988 was a leap year.
```{r}
(dmy("01-01-1988")%--%dmy("01-01-1989"))%/%days(366)
```
## 3 Use and show R coding to confirm that the year 1989 was a not a leap year.
```{r}
(dmy("01-01-1989")%--%dmy("01-01-1990"))%/%days(365)
```

## 4 Why is there months() but no dmonths ? 

ddays, dmins,dweeks etc converts number of days,mins,weeks into seconds because there sizes are constant, they do not change. when we talk about months there values are different. For instance in january there are 31 days and in february there are 28 days. So there size differs, it difficult for the system to understand.  

## 5) John was born April 11th, 1962. Use and show R coding to determine how old John is in 
years
```{r}
(dmy("11-04-1962")%--%today())%/%years(1)
```

## 6) Modify the flights_dt coding in the notes or the book to obtain the following partial data 
table shown below.  Show all required coding. (Most of the coding needed is provided in the 
notes)  

```{r}
make_datetime_100 <- function(year, month, day, time) {
  make_datetime(year, month, day, time %/% 100, time %% 100)
}
flights %>% 
  filter(!is.na(dep_time), !is.na(arr_time)) %>% 
  mutate(
    dep_time = make_datetime_100(year, month, day, dep_time),
    arr_time = make_datetime_100(year, month, day, arr_time),
    sched_dep_time = make_datetime(year, month, day, sched_dep_time),
    sched_arr_time = make_datetime(year, month, day, sched_arr_time)
  ) %>% 
  select(origin, dest, carrier,arr_time,dep_time) ->

flights_dt

flights_dt
```


## 7) Now, using your table from #6, produce the frequency plot shown which conveys frequency 
counts for the months of April, July, and October for the year 2013
```{r}
flights_dt%>%
  filter(year(dep_time)==2013&month(dep_time)>3&month(dep_time)<11)%>%
  ggplot(mapping = aes(x=dep_time))+
  geom_freqpoly(bins=94)

```
## 8 Now use dplyr functions to produce a data table that shows arrival times for American 
Airlines at the Dallas Fort Worth Airport from the LaGuardia airport in New York. Your output 
should show rows 115 to 125.  

```{r}
flights_dt%>%
  filter(carrier=='AA',origin=='LGA',dest=='DFW')%>%
  slice(115:125)%>%
  select(-dep_time)->new_flights

new_flights
```
## 9 Using the first two observational date time designations from your #8 table, Use and show R 
code to confirm that there are 181 minutes time intervals between them.  

```{r}
first=new_flights['arr_time'][1,]
second=new_flights['arr_time'][2,]
dhours(second-first)/dminutes(1)
```

